\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
Tune discussion of full abstraction a bit.

\section{Discussion}
\label{sec:discussion}
% \begin{itemize}
% \item explain how fully abstract overlay semantics could form one pass of a verified secure compiler.
% \item Sharing stack references accross component boundaries is supported
% \item Other notions of well-bracketedness (specifically one would be to allow different stacks)
% \end{itemize}
\subsection{Full abstraction}
% - Full abstraction proofs difficult
In the grand scheme of proving full abstraction from a high-level language to assembly, we believe \stktokens{} can play a role.
The target of a fully-abstract compiler must have enforcement mechanisms that can enforce the properties of the high-level language.
As demonstrated in this paper, a capability machine with linear capabilities can enforce two such properties namely LSE and WBCF.
Further due to the modularity of full-abstraction proofs, fully abstract compilers from languages with LSE and WBCF can target \srccm{} directly and rely on the full-abstraction proof this paper presents.
However in order for a fully abstract compiler utilise our full-abstraction proof, it must satisfy the conditions of the proof, namely the compiled code must be well-formed and well-behaved.
From a high-level perspective this condition actually says that the compiled code does not need to protect itself from itself which it would have to without the condition.

When creating fully-abstract compilers between low-level machines, it is a big challenge to work with the exposed addresses.
In particular, if the compilation changes the code size of a block of code, then it may be observable and prevent full-abstraction from being proven.
We would argue that when a compilation reaches a phase where addresses are exposed, then the compilation should no longer change the code.
This does, however, pose the challenge that there might quite a few abstractions in difference between the language where addresses are hidden to a machine where they are not.
We propose that this challenge is solved by implementing these abstractions in a number of overlay semantics.
By implementing them one by one, one can deal with one abstraction at a time reducing the complexity of each necessary full-abstraction proof.

>>>>

\section{Discussion}
\label{sec:discussion}
% \begin{itemize}
% \item explain how fully abstract overlay semantics could form one pass of a verified secure compiler.
% \item Sharing stack references accross component boundaries is supported
% \item Other notions of well-bracketedness (specifically one would be to allow different stacks)
% \end{itemize}
\subsection{Full abstraction}
% - Full abstraction proofs difficult
Our formulation of WBCF and LSE using a fully abstract overlay semantics has an advantage with respect to others that we haven't discussed yet.
Imagine that you are implementing a fully abstract compiler for a high-level language, i.e.\ a secure compiler that enforces high-level abstractions when interacting with untrusted target-language components.
Such a compiler would need to perform many things and enforce other high-level properties than just WBCF and LSE.

If such a compiler uses the \stktokens{} calling convention, then the security proof should not have to reprove security of \stktokens{}.
Ideally, it should just combine security proofs for the compiler's other functionality with our results about \stktokens{}.
We want to point out that our formulation enables such reuse.
Specifically, the compiler could be factored into a part that targets \srccm{}, followed by our embedding into \trgcm{}.
If the authors of the secure compiler can prove full abstraction of the first part (relying on WBCF and LSE in \srccm{}) and they can also prove that this first part generates well-formed and reasonable components, then full abstraction of the whole compiler follows by our result and transitivity of fully abstract compilation.
Perhaps other reusable components of secure compilers could be formulated similarly using some form of fully abstract overlay semantics, to obtain similar reusability of their security proofs.

% When creating fully-abstract compilers between low-level machines, it is a big challenge to work with the exposed addresses.
% In particular, if the compilation changes the code size of a block of code, then it may be observable and prevent full-abstraction from being proven.
% We would argue that when a compilation reaches a phase where addresses are exposed, then the compilation should no longer change the code.
% This does, however, pose the challenge that there might quite a few abstractions in difference between the language where addresses are hidden to a machine where they are not.
% We propose that this challenge is solved by implementing these abstractions in a number of overlay semantics.
% By implementing them one by one, one can deal with one abstraction at a time reducing the complexity of each necessary full-abstraction proof.
